Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Title case
Formatting

\subsection{Stage 4: orienting matches}
The final stage, stage 4, orients skippers within matches, such that they are either port (red) or starboard (green). This is done to satisfy criteria 2 and 3, 5 and 8. A sketch of the constraint model is given with a supporting diagram, Figure \ref{oriented}.  A sequence of zero/one constrained integer variables, of length $n-1$, is produced for each skipper. These correspond to the sequence of skippers they meet in matches. For example, taking the schedule in Table \ref{tab2}, skipper $\sigma[{2}]$ meets skippers in the following order: 3,0,1,4,5,6 and skipper $\sigma[{5}]$ in the order: 4,6,0,1,3,2. Therefore, skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from $\sigma[{5}]$ 5$^{th}$ variable. There are summation constraints on each skipper to enforce criteria 2 and 3 (equal number of port and starboard matches). Criteria 8 is enforced by posting constraints such that in a match ($\sigma[{i}],\sigma[{j}]$) where $|i - j| = 1$ the higher indexed skipper (lower ranked) is on the port side. A deterministic finite automata constraint is posted for criteria 5 (restricting sequences of port and starboard assignments).

>>>>

\subsection{Stage 4: Orienting Matches}

The final stage, stage 4, orients skippers within matches, such that they are
either port (red) or starboard (green). This is done to satisfy criteria 2 and
3, 5 and 8. A sketch of the constraint model is given with a supporting
diagram, Figure~\ref{oriented}.  A sequence of zero/one constrained integer
variables, of length $n-1$, is produced for each skipper. These correspond to
the sequence of skippers they meet in matches. For example, taking the schedule
in Table~\ref{tab2}, skipper $\sigma[{2}]$ meets skippers in order:
3,0,1,4,5,6, and skipper $\sigma[{5}]$ in the order 4,6,0,1,3,2.  Therefore,
skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from
$\sigma[{5}]$ 5$^{th}$ variable. There are summation constraints on each
skipper to enforce criteria 2 and 3 (equal number of port and starboard
matches). Criteria 8 is enforced by posting constraints such that in a match
($\sigma[{i}],\sigma[{j}]$) where $|i - j| = 1$, the higher indexed skipper
(lower ranked) is on the port side. A DFA constraint is posted for criteria 5
(restricting sequences of port and starboard assignments).
